---
title: "Mice"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The purpose of this problem is to build intuition for the bootstrap procedure. With that in mind, 
consider the very small data set of the weights of three mice that came from the same litter. The 
weights are 82, 107 and 93 grams.

```{r}
weights <- c(82, 107, 93)
```

* What is the mean weight of the three mice?
* How many possible bootstrap samples are there from this sample of three mice?
* List all possible bootstrap samples and compute the mean of each.
* Compute the mean of the bootstrap means. How does this compare with the mean from part (a)?
* Calculate a percentile-based bootstrap confidence interval with level of confidence at least 95%.
  What information does this interval provide? How confident are you in reporting this interval?
  Explain.

```{r}
mean(weights)
```

The mean weight of the three mice is 94.

```{r}
samps <- expand.grid(weights, weights, weights)

nrow(samps)
```

There are 27 possible bootstrap samples.

```{r}
samps$Mean <- rowMeans(samps)

samps
```

```{r}
mean(samps$Mean)
```

The mean of all the possible bootstrap samples is the same as the mean for the three mice (94).

```{r}
quantile(samps$Mean, probs = c(0.025, 0.975))
```

This interval provides a 95% confidence interval on the average weight of the mice population
that these mice were taken from (assuming it is a representative sample). However, since the sample
size is so small, I'm not very confident in reporting this interval.