---
title: "Trees"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the trees dataset found in R, there are three variables “Girth” “Height” and “Volume”. There is 
interest in using “Girth” and “Height” (two noninvasive measures) to predict “Volume”. Carrying out
this prediction can be done using a regression model with two explanatory variables (“Height” and
“Girth”).

Principal interest lies in estimating the regression coefficient of “Height” divided by the regression
coefficient for “Girth”. Obtaining an estimate of the ratio is easy — just compute the ratio of the
two slope estimates — but assessing uncertainty associated with the point estimate can be difficult 
theoretically (although methods do exist).

* For this problem construct a 95% confidence interval using the bootstrap procedure. Use 5,000
  bootstrap samples. Compute your estimate and confidence bounds.
  
***

Let's take a look at the trees dataset.
```{r}
head(trees)
```

Create a function 'tree_bs' which calculates a bootstrap sample from the 'trees' data, runs the
regression of 'Volume' on 'Girth' and 'Height', and calculates the ratio of the 'Height' coefficient
to the 'Girth' coefficient.
```{r}
tree_bs <- function() {
  
  bs_sample <- trees[sample(nrow(trees), nrow(trees), replace = TRUE),]

  mdl <- lm(Volume ~ Girth + Height, data = bs_sample)

  girth_coeff <- summary(mdl)$coefficients[2, 1]
  height_coeff <- summary(mdl)$coefficients[3, 1]

  return(height_coeff / girth_coeff)
  
}
```

Run the 'tree_bs' function 5000 times to create 5000 estimates of the ratio calculated using
the bootstrap procedure. Calculate an estimate of the mean ratios from the bootstrapped ratios and a
95% confidence interval around that mean ratio.
```{r}
bs_coeffs <- replicate(5000, tree_bs())

mean(bs_coeffs)
quantile(bs_coeffs, probs = c(0.025, 0.975))
```